Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond

### 2024-01-03 abstract.tex
:pencil: Add abstract

\begin{document}
\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		Hongyu~Li,~\IEEEmembership{Graduate Student Member,~IEEE,}\\
		Yijie~Mao,~\IEEEmembership{Member,~IEEE,}
		Shanpu~Shen,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	% \thanks{
	% 	The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	% 	B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
	% }
}
\maketitle

>>>>

\begin{document}
\title{Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		Hongyu~Li,~\IEEEmembership{Graduate Student Member,~IEEE,}\\
		Massimo~Franceschetti,~\IEEEmembership{Fellow,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	% \thanks{
	% 	The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	% 	B. Clerckx is also with Silicon Austria Labs (SAL), Graz A-8010, Austria.
	% }
}
\maketitle
